Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-09 article/article.tex
Diving Bell

ROI mapping. As described in the introduction, ROIs are anatomically defined brain areas classified as relevant by an expert in the field. To reduce the number of features, average voxel values within this regions are taken as input features. As other higher-order features  such as the standard deviation, kurtosis and skweness within ROIs did not increase predictability, these were not utilized.

>>>>

ROI mapping. As described in the introduction, ROIs are anatomically defined brain areas classified as relevant by an expert in the field. To reduce the number of features, average voxel values within this regions are taken as input features. As other higher-order features such as the standard deviation, kurtosis and skewness within ROIs did not increase predictability, these were not utilized.
